EldersAIR: Main analysis - PM/Exposure Outcomes

### 2021-05-07 main_analysis_pm.Rmd
fibit data cleaning new interaction analysis

---
title: 'EldersAIR: Main analysis - PM/Exposure Outcomes'
author: "Ethan Walker"
date: "Started 6 May 2021; Updated 6 May 2021"
output: pdf_document
---

@@

elders_cleaned_dataset_by_visit <- read_rds(paste0(file_path, "Output/elders_cleaned_dataset_by_visit.rds")) 
```

```{r}
analysis_data <- elders_cleaned_dataset_by_visit %>% 
  mutate(treatment = factor(treatment,
                            levels = c("Placebo", "Filter", "Education"),
                            labels = c("Placebo", "Filter", "Education")),
         visit_intervention_diff = round(difftime(sampling_date, intervention_date, 
                                            units = "days"), digits = 0),
         visit_intervention_diff = as.numeric(visit_intervention_diff),
         visit_intervention_diff = if_else(winter_id == 1, 9999,
                                           visit_intervention_diff)) %>% 
  # All but 4 homes (all NPT homes that used Large Filtretes) in the Filter arm used Winix units
  # Filter type isn't really feasible to use in the analysis due to this small sample size
  mutate(treatment_filter_type = as.character(treatment),
         filter_type = as.character(filter_type),
         treatment_filter_type2 = if_else(treatment_filter_type == "Filter", filter_type,
                                         treatment_filter_type),
         treatment_filter_type = factor(treatment_filter_type2,
                                        levels = c("Placebo", "Education",
                                                   "Large Filtrete", "Winix")),
         filter_type = as.factor(filter_type),
         kw_perc_expected = if_else(treatment == "Education", 100, kw_perc_expected)) %>% 
  mutate(treatment = as.character(treatment),
         perc_exp_quart = cut(kw_perc_expected,
                                  breaks = c(0, 25, 46, 71, 1000),
                                  labels = c("0-25 compliance", "25-50 compliance",
                                             "50-75 compliance", "75-100 compliance")),
         perc_exp_quart = as.character(perc_exp_quart),
         filter_compliance = if_else(treatment == "Filter",
                                     perc_exp_quart, 
                                     treatment),
         treatment = factor(treatment,
                            levels = c("Placebo", "Education", "Filter")),
         filter_compliance = factor(filter_compliance,
                                    levels = c("Placebo", "Education",
                                               "0-25 compliance", "25-50 compliance",
                                               "50-75 compliance", "75-100 compliance"))) %>% 
  select(-treatment_filter_type2) 
```

# Indoor/Area PM2.5
```{r}
pm_data_2row <- analysis_data %>% 
  mutate(outcome = pm_mean_visit) %>%  # select outcome here
  arrange(area, home, adult_id_char, winter_id, sampling_visit) %>% 
  group_by(area, home, adult_id_char, winter_id) %>% 
  mutate(outcome = if_else(winter_id == 1, mean(outcome, na.rm = T), outcome)) %>% 
  dplyr::select(area, home, adult_id_char, winter_id, sampling_visit, 
                cohort, treatment, outcome, income, education, residents_smoke, 
                home_sqm_2level, burn_level, gender, chimney_clean, stove_age, 
                stove_grade, age, bmi, visit_intervention_diff,
                treatment_filter_type, filter_compliance, kw_perc_expected) %>% 
  ungroup() %>% 
  distinct(area, home, winter_id, sampling_visit, .keep_all = T) %>% 
  group_by(area, home) %>% 
  pivot_wider(names_from = "winter_id", values_from = "outcome") %>% 
  arrange(area, home, sampling_visit) %>% 
  mutate(outcome = `2`,
         baseline_outcome = `1`,
         baseline_outcome = if_else(is.na(baseline_outcome), first(baseline_outcome),
                                    baseline_outcome)) %>% 
  replace_with_na(replace = list(baseline_outcome = NaN, outcome = NaN)) %>% 
  filter(visit_intervention_diff != 9999) %>% 
  ungroup()

pm_at_home_data <- analysis_data %>% 
  mutate(outcome = pm_mean_at_home_visit) %>%  # select outcome here
  arrange(area, home, adult_id_char, winter_id, sampling_visit) %>% 
  group_by(area, home, adult_id_char, winter_id) %>% 
  mutate(outcome = if_else(winter_id == 1, mean(outcome, na.rm = T), outcome)) %>% 
  dplyr::select(area, home, adult_id_char, winter_id, sampling_visit, 
                cohort, treatment, outcome, income, education, residents_smoke, 
                home_sqm_2level, burn_level, gender, chimney_clean, stove_age, 
                stove_grade, age, bmi, visit_intervention_diff,
                treatment_filter_type, filter_compliance, kw_perc_expected) %>% 
  ungroup() %>% 
  distinct(area, adult_id_char, winter_id, sampling_visit, .keep_all = T) %>% 
  group_by(area, adult_id_char) %>% 
  pivot_wider(names_from = "winter_id", values_from = "outcome") %>% 
  arrange(area, adult_id_char, sampling_visit) %>% 
  mutate(outcome = `2`,
         baseline_outcome = `1`,
         baseline_outcome = if_else(is.na(baseline_outcome), first(baseline_outcome),
                                    baseline_outcome)) %>% 
  replace_with_na(replace = list(baseline_outcome = NaN, outcome = NaN)) %>% 
  filter(visit_intervention_diff != 9999) %>% 
  ungroup()

@@

@@

tidy_results_primary <- tidy(itt_pm_results_primary, conf.int = TRUE) %>% 
  mutate(group_filter = if_else(grepl("treatment", term), 1, 0)) %>% 
  filter(group_filter == 1) %>% 
  mutate(term = gsub("treatment", "", term)) %>% 
  mutate(estimate = round((exp(estimate)-1)*100, digits = 2),
         conf.low = round((exp(conf.low)-1)*100, digits = 2),
         conf.high = round((exp(conf.high)-1)*100, digits = 2),
         p.value = round((p.value), digits = 2)) %>% 
  dplyr::select(term, estimate, conf.low, conf.high, p.value) %>% 
  mutate(term = gsub("treatment", "", term),
         model = "Primary") 
kable(tidy_results_primary)

@@

itt_pm_results_confounders <- lmer(log(outcome) ~ treatment + 
                                education + residents_smoke + home_sqm_2level +
                                burn_level + gender + chimney_clean + stove_grade + 
                                age + bmi + 
                                baseline_outcome + (1 | home:cohort:area), 
                                data = pm_data_2row)

@@

# Personal PM2.5
```{r}
pm_data_2row <- analysis_data %>% 
  mutate(outcome = mp_mean_visit) %>%  # select outcome here
  arrange(area, home, adult_id_char, winter_id, sampling_visit) %>% 
  group_by(area, home, adult_id_char, winter_id) %>% 
  mutate(outcome = if_else(winter_id == 1, mean(outcome, na.rm = T), outcome)) %>% 
  dplyr::select(area, home, adult_id_char, winter_id, sampling_visit, 
                cohort, treatment, outcome, income, education, residents_smoke, 
                home_sqm_2level, burn_level, gender, chimney_clean, stove_age, 
                stove_grade, age, bmi, visit_intervention_diff,
                treatment_filter_type, filter_compliance, kw_perc_expected) %>% 
  ungroup() %>% 
  distinct(area, home, winter_id, sampling_visit, .keep_all = T) %>% 
  group_by(area, home) %>% 
  pivot_wider(names_from = "winter_id", values_from = "outcome") %>% 
  arrange(area, home, sampling_visit) %>% 
  mutate(outcome = `2`,
         baseline_outcome = `1`,
         baseline_outcome = if_else(is.na(baseline_outcome), first(baseline_outcome),
                                    baseline_outcome)) %>% 
  replace_with_na(replace = list(baseline_outcome = NaN, outcome = NaN)) %>% 
  filter(visit_intervention_diff != 9999) %>% 
  ungroup()

@@

@@

itt_pm_results_confounders <- lmer(log(outcome) ~ treatment + 
                                education + residents_smoke + home_sqm_2level +
                                burn_level + gender + chimney_clean + stove_grade + 
                                age + bmi + 
                                baseline_outcome + (1 | adult_id_char:home:cohort), 
                                data = pm_data_2row)

@@

tidy_results_combined <- rbind(tidy_results_primary, tidy_results_filter_type,
                               #tidy_results_filter_compliance, 
                               tidy_results_confounders)

@@

itt_plot_estimates <- tidy_results_combined %>%
  mutate(model = factor(model,
                        levels = c("Primary", "Filter Type", 
                                   #"Filter Compliance", 
                                   "Confounders"))) %>% 
  ggplot(aes(group = term, shape = term)) +
    geom_point(aes(x=model, y=estimate), 
               position = position_dodge(width = 0.5), size = 4) +
    geom_errorbar(aes(x=model, ymin=conf.low, ymax=conf.high), 
                  position = position_dodge(width = 0.5), size = 1.2, width = 0.5) +
    geom_hline(yintercept = 0) +
    theme_bw() +  
    ggtitle(label = "PM Model - ITT framework",
            subtitle = "ICC for Household = 0.41") +
    labs(y = "% difference compared to Placebo") +
    labs(x = "", group = "", shape = "") +
    theme(title = element_text(size = 16), 
          axis.text.x = element_text(size = 16, colour = "black", angle = 45,
                                     hjust = 1, vjust = .8),
          axis.text.y = element_text(size = 16, colour = "black"),
          axis.title.y = element_text(size = 16,
                                      margin = margin(t = 0, r = 20, b = 0, l = 0)),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank(), 
          panel.border = element_blank(), 
          panel.grid = element_blank(),
          legend.position = "top",
          legend.text = element_text(size = 14, colour = "black")) 
itt_plot_estimates

@@

# Indoor/Area PM2.5 Interaction Analysis
```{r}
# Prep Data
pm_data_2row <- analysis_data %>% 
  mutate(outcome = pm_mean_visit) %>%  # select outcome here
  arrange(area, home, adult_id_char, winter_id, sampling_visit) %>% 
  group_by(area, home, adult_id_char, winter_id) %>% 
  mutate(outcome = if_else(winter_id == 1, mean(outcome, na.rm = T), outcome)) %>% 
  dplyr::select(area, home, adult_id_char, winter_id, sampling_visit, 
                cohort, treatment, outcome, income, education, residents_smoke, 
                home_sqm_2level, burn_level, gender, chimney_clean, stove_age, 
                stove_grade, age, bmi, visit_intervention_diff, home_floors_2level,
                treatment_filter_type, filter_compliance, kw_perc_expected,
                home_year_built_2level, wood_collect, wood_collect_method) %>% 
  ungroup() %>% 
  distinct(area, home, winter_id, sampling_visit, .keep_all = T) %>% 
  group_by(area, home) %>% 
  pivot_wider(names_from = "winter_id", values_from = "outcome") %>% 
  arrange(area, home, sampling_visit) %>% 
  mutate(outcome = `2`,
         baseline_outcome = `1`,
         baseline_outcome = if_else(is.na(baseline_outcome), first(baseline_outcome),
                                    baseline_outcome)) %>% 
  replace_with_na(replace = list(baseline_outcome = NaN, outcome = NaN)) %>% 
  filter(visit_intervention_diff != 9999) %>% 
  ungroup()

@@

save_contrasts <<- confint(int_emmeans$contrasts) %>% 
  mutate(estimate = round((exp(estimate)), digits = 2),
         conf.low = round((exp(lower.CL)), digits = 2),
         conf.high = round((exp(upper.CL)), digits = 2)) %>% 
  dplyr::select(contrast, int_var, estimate, conf.low, conf.high)

@@

plot_results <- save_contrasts %>% 
  ggplot(aes(group = contrast, shape = contrast)) +
  geom_point(aes(x=int_var, y=estimate), 
             position = position_dodge(width = 0.5), size = 4) +
  geom_errorbar(aes(x=int_var, ymin=conf.low, ymax=conf.high), 
             position = position_dodge(width = 0.5), size = 1.2, width = 0.5) +
  geom_hline(yintercept = 1) +
  theme_bw() +  
  ggtitle(label = "Interaction contrasts for ITT framework, PM outcome",
          subtitle = paste0("Interaction term = ", interaction_label)) +
  labs(y = "% difference vs placebo") +
  labs(x = "", group = "", shape = "") +
  theme(title = element_text(size = 16), 
          axis.text.x = element_text(size = 16, colour = "black", angle = 45,
                                     hjust = 1, vjust = .8),
          axis.text.y = element_text(size = 16, colour = "black"),
          axis.title.y = element_text(size = 16,
                                      margin = margin(t = 0, r = 20, b = 0, l = 0)),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank(), 
          panel.border = element_blank(), 
          panel.grid = element_blank(),
          legend.position = "top",
          legend.text = element_text(size = 14, colour = "black"))

@@

# Try: home_floors_2level, home_sqm_2level, education, income,
# home_year_built_2level, stove_age, stove_grade, chimney_clean,
# wood_collect, wood_collect_method, burn_level, residents_smoke
int_function(pm_data_2row, "home_floors_2level", "Floors in home")
int_function(pm_data_2row, "home_sqm_2level", "Home Square Meters")
int_function(pm_data_2row, "education", "Education")
int_function(pm_data_2row, "income", "Income")
int_function(pm_data_2row, "home_year_built_2level", "Year home was built")
int_function(pm_data_2row, "stove_age", "Stove age")
int_function(pm_data_2row, "stove_grade", "Stove grade")
int_function(pm_data_2row, "chimney_clean", "When was chimney cleaned")
int_function(pm_data_2row, "wood_collect", "When was wood collected")
int_function(pm_data_2row, "wood_collect_method", "Wood collect method")
int_function(pm_data_2row, "burn_level", "Burn level")
int_function(pm_data_2row, "residents_smoke", "Residents Smoke")

n_table
save_contrasts
pm_summary_table
save_summary
save_contrasts_full
obs <- pm_data_2row %>% 
  filter(!is.na(outcome)) %>% 
  filter(!is.na(baseline_outcome)) %>%
  filter(!is.na(area)) %>% 
  filter(!is.na(cohort)) %>% 
  filter(!is.na(treatment)) %>% 
  filter(!is.na(residents_smoke)) %>%
  group_by(residents_smoke, treatment) %>% 
  count()
obs
Anova(itt_results_int)

@@

>>>>

---
title: 'EldersAIR: Main analysis - PM/Exposure Outcomes'
author: "Ethan Walker"
date: "Started 6 May 2021; Updated 7 May 2021"
output: pdf_document
---

@@

analysis_data <- read_rds(paste0(file_path, "Output/elders_cleaned_dataset_by_visit.rds")) 
```

# Indoor/Area PM2.5
```{r}
pm_data_2row <- analysis_data %>% 
  mutate(outcome = pm_mean_visit) %>%  # select outcome here
  arrange(area, home, adult_id_char, winter_id, sampling_visit) %>% 
  group_by(area, home, adult_id_char, winter_id) %>% 
  mutate(outcome = if_else(winter_id == 1, mean(outcome, na.rm = T), outcome)) %>% 
  dplyr::select(area, home, adult_id_char, winter_id, sampling_visit, 
                cohort, treatment, outcome, income, education, residents_smoke, 
                home_sqm_2level, burn_level, gender, chimney_clean, stove_age, 
                stove_grade, age, bmi, visit_intervention_diff,
                treatment_filter_type, filter_compliance, kw_perc_expected,
                burn_level_3level, chimney_clean_3level, age_2level,
                bmi_2level, income_2level, income_3level, stove_age_2level,
                steps, steps_2level, steps_4level,
                hypertension, wood_collect_3level) %>% 
  ungroup() %>% 
  distinct(area, home, winter_id, sampling_visit, .keep_all = T) %>% 
  group_by(area, home) %>% 
  pivot_wider(names_from = "winter_id", values_from = "outcome") %>% 
  arrange(area, home, sampling_visit) %>% 
  mutate(outcome = `2`,
         baseline_outcome = `1`,
         baseline_outcome = if_else(is.na(baseline_outcome), first(baseline_outcome),
                                    baseline_outcome)) %>% 
  replace_with_na(replace = list(baseline_outcome = NaN, outcome = NaN)) %>% 
  filter(visit_intervention_diff != 9999) %>% 
  ungroup()

pm_at_home_data <- analysis_data %>% 
  mutate(outcome = pm_mean_at_home_visit) %>%  # select outcome here
  arrange(area, home, adult_id_char, winter_id, sampling_visit) %>% 
  group_by(area, home, adult_id_char, winter_id) %>% 
  mutate(outcome = if_else(winter_id == 1, mean(outcome, na.rm = T), outcome)) %>% 
  dplyr::select(area, home, adult_id_char, winter_id, sampling_visit, 
                cohort, treatment, outcome, income, education, residents_smoke, 
                home_sqm_2level, burn_level, gender, chimney_clean, stove_age, 
                stove_grade, age, bmi, visit_intervention_diff,
                treatment_filter_type, filter_compliance, kw_perc_expected,
                burn_level_3level, chimney_clean_3level, age_2level,
                bmi_2level, income_2level, income_3level, stove_age_2level,
                steps, steps_2level, steps_4level,
                hypertension, wood_collect_3level) %>% 
  ungroup() %>% 
  distinct(area, adult_id_char, winter_id, sampling_visit, .keep_all = T) %>% 
  group_by(area, adult_id_char) %>% 
  pivot_wider(names_from = "winter_id", values_from = "outcome") %>% 
  arrange(area, adult_id_char, sampling_visit) %>% 
  mutate(outcome = `2`,
         baseline_outcome = `1`,
         baseline_outcome = if_else(is.na(baseline_outcome), first(baseline_outcome),
                                    baseline_outcome)) %>% 
  replace_with_na(replace = list(baseline_outcome = NaN, outcome = NaN)) %>% 
  filter(visit_intervention_diff != 9999) %>% 
  ungroup()

@@

table(model.frame(itt_pm_results_primary)$treatment)

nobs(itt_pm_results_primary)

@@

tidy_results_primary <- tidy(itt_pm_results_primary, conf.int = TRUE) %>% 
  mutate(group_filter = if_else(grepl("treatment", term), 1, 0)) %>% 
  filter(group_filter == 1) %>% 
  mutate(term = gsub("treatment", "", term)) %>% 
  mutate(estimate = round((exp(estimate)-1)*100, digits = 2),
         conf.low = round((exp(conf.low)-1)*100, digits = 2),
         conf.high = round((exp(conf.high)-1)*100, digits = 2),
         p.value = round((p.value), digits = 2)) %>% 
  dplyr::select(term, estimate, conf.low, conf.high, p.value) %>% 
  mutate(term = gsub("treatment", "", term),
         model = "Primary") 
#kable(tidy_results_primary)

@@

itt_pm_results_confounders <- lmer(log(outcome) ~ treatment + 
                                education + residents_smoke + home_sqm_2level +
                                burn_level_3level + gender + chimney_clean_3level + 
                                stove_grade + age + bmi + 
                                baseline_outcome + (1 | home:cohort:area), 
                                data = pm_data_2row)

@@

# Personal PM2.5
```{r}
pm_data_2row <- analysis_data %>% 
  mutate(outcome = mp_mean_visit) %>%  # select outcome here
  arrange(area, home, adult_id_char, winter_id, sampling_visit) %>% 
  group_by(area, home, adult_id_char, winter_id) %>% 
  mutate(outcome = if_else(winter_id == 1, mean(outcome, na.rm = T), outcome)) %>% 
  dplyr::select(area, home, adult_id_char, winter_id, sampling_visit, 
                cohort, treatment, outcome, income, education, residents_smoke, 
                home_sqm_2level, burn_level, gender, chimney_clean, stove_age, 
                stove_grade, age, bmi, visit_intervention_diff,
                treatment_filter_type, filter_compliance, kw_perc_expected,
                burn_level_3level, chimney_clean_3level, age_2level,
                bmi_2level, income_2level, income_3level, stove_age_2level,
                steps, steps_2level, steps_4level,
                hypertension, wood_collect_3level) %>% 
  ungroup() %>% 
  distinct(area, home, winter_id, sampling_visit, .keep_all = T) %>% 
  group_by(area, home) %>% 
  pivot_wider(names_from = "winter_id", values_from = "outcome") %>% 
  arrange(area, home, sampling_visit) %>% 
  mutate(outcome = `2`,
         baseline_outcome = `1`,
         baseline_outcome = if_else(is.na(baseline_outcome), first(baseline_outcome),
                                    baseline_outcome)) %>% 
  replace_with_na(replace = list(baseline_outcome = NaN, outcome = NaN)) %>% 
  filter(visit_intervention_diff != 9999) %>% 
  ungroup()

@@

#table(model.frame(itt_pm_results_primary)$treatment)

#nobs(itt_pm_results_primary)

@@

itt_pm_results_fitbit_steps <- lmer(log(outcome) ~ treatment + steps_4level + 
                                baseline_outcome + (1 | adult_id_char:home:cohort), 
                                data = pm_data_2row)

tidy_results_fitbit_steps <- tidy(itt_pm_results_fitbit_steps, conf.int = TRUE) %>% 
  mutate(group_filter = if_else(grepl("treatment", term), 1, 0)) %>% 
  filter(group_filter == 1) %>% 
  mutate(term = gsub("treatment", "", term)) %>% 
  mutate(estimate = round((exp(estimate)-1)*100, digits = 2),
         conf.low = round((exp(conf.low)-1)*100, digits = 2),
         conf.high = round((exp(conf.high)-1)*100, digits = 2),
         p.value = round((p.value), digits = 2)) %>% 
  dplyr::select(term, estimate, conf.low, conf.high, p.value) %>% 
  mutate(model = "Fitbit Steps")

itt_pm_results_confounders <- lmer(log(outcome) ~ treatment + 
                                education + residents_smoke + home_sqm_2level +
                                burn_level_3level + gender + chimney_clean_3level + 
                                stove_grade + age + bmi + 
                                baseline_outcome + (1 | adult_id_char:home:cohort), 
                                data = pm_data_2row)

@@

# Calculate ICC
## The ratio of the between-cluster variance to the total variance
## It can also be interpreted as the correlation among observations within the same cluster
icc_model <- lmer(outcome ~ (1 | adult_id_char), pm_data_2row)
pm_icc <- icc(icc_model)

tidy_results_combined <- rbind(tidy_results_primary, tidy_results_filter_type,
                               #tidy_results_filter_compliance, 
                               tidy_results_fitbit_steps,
                               tidy_results_confounders)

@@

itt_plot_estimates <- tidy_results_combined %>%
  mutate(model = factor(model,
                        levels = c("Primary", "Filter Type", 
                                   #"Filter Compliance", 
                                   "Fitbit Steps",
                                   "Confounders"))) %>% 
  ggplot(aes(group = term, shape = term)) +
    geom_point(aes(x=model, y=estimate), 
               position = position_dodge(width = 0.5), size = 4) +
    geom_errorbar(aes(x=model, ymin=conf.low, ymax=conf.high), 
                  position = position_dodge(width = 0.5), size = 1.2, width = 0.5) +
    geom_hline(yintercept = 0) +
    theme_bw() +  
    ggtitle(label = "PM Model - ITT framework",
            subtitle = "ICC for Participant = 0.41") +
    labs(y = "% difference compared to Placebo") +
    labs(x = "", group = "", shape = "") +
    theme(title = element_text(size = 16), 
          axis.text.x = element_text(size = 16, colour = "black", angle = 45,
                                     hjust = 1, vjust = .8),
          axis.text.y = element_text(size = 16, colour = "black"),
          axis.title.y = element_text(size = 16,
                                      margin = margin(t = 0, r = 20, b = 0, l = 0)),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank(), 
          panel.border = element_blank(), 
          panel.grid = element_blank(),
          legend.position = "top",
          legend.text = element_text(size = 14, colour = "black")) 
itt_plot_estimates

@@

# Indoor/Area PM2.5 Interaction Analysis
```{r}
# Prep Data
pm_data_2row <- analysis_data %>% 
  mutate(outcome = pm_mean_visit) %>%  # select outcome here
  arrange(area, home, adult_id_char, winter_id, sampling_visit) %>% 
  group_by(area, home, adult_id_char, winter_id) %>% 
  mutate(outcome = if_else(winter_id == 1, mean(outcome, na.rm = T), outcome)) %>% 
  dplyr::select(area, home, adult_id_char, winter_id, sampling_visit, 
                cohort, treatment, outcome, income, education, residents_smoke, 
                home_sqm_2level, burn_level, gender, chimney_clean, stove_age, 
                stove_grade, age, bmi, visit_intervention_diff, 
                treatment_filter_type, filter_compliance, kw_perc_expected,
                burn_level_3level, chimney_clean_3level, age_2level,
                bmi_2level, income_2level, income_3level, stove_age_2level,
                hypertension, wood_collect_3level, home_year_built_2level,
                steps, steps_2level, steps_4level,
                home_floors_2level, wood_collect_method) %>% 
  ungroup() %>% 
  distinct(area, home, winter_id, sampling_visit, .keep_all = T) %>% 
  group_by(area, home) %>% 
  pivot_wider(names_from = "winter_id", values_from = "outcome") %>% 
  arrange(area, home, sampling_visit) %>% 
  mutate(outcome = `2`,
         baseline_outcome = `1`,
         baseline_outcome = if_else(is.na(baseline_outcome), first(baseline_outcome),
                                    baseline_outcome)) %>% 
  replace_with_na(replace = list(baseline_outcome = NaN, outcome = NaN)) %>% 
  filter(visit_intervention_diff != 9999) %>% 
  ungroup()

@@

save_contrasts <<- confint(int_emmeans$contrasts) %>% 
  mutate(estimate = round((exp(estimate)-1)*100, digits = 2),
         conf.low = round((exp(lower.CL)-1)*100, digits = 2),
         conf.high = round((exp(upper.CL)-1)*100, digits = 2)) %>% 
  dplyr::select(contrast, int_var, estimate, conf.low, conf.high)

@@

plot_results <- save_contrasts %>% 
  ggplot(aes(group = contrast, shape = contrast)) +
  geom_point(aes(x=int_var, y=estimate), 
             position = position_dodge(width = 0.5), size = 4) +
  geom_errorbar(aes(x=int_var, ymin=conf.low, ymax=conf.high), 
             position = position_dodge(width = 0.5), size = 1.2, width = 0.5) +
  geom_hline(yintercept = 1) +
  theme_bw() +  
  ggtitle(label = "Interaction contrasts, ITT framework, Area PM",
          subtitle = paste0("Interaction term = ", interaction_label)) +
  labs(y = "% difference") +
  labs(x = "", group = "", shape = "") +
  theme(title = element_text(size = 16), 
          axis.text.x = element_text(size = 16, colour = "black", angle = 45,
                                     hjust = 1, vjust = .8),
          axis.text.y = element_text(size = 16, colour = "black"),
          axis.title.y = element_text(size = 16,
                                      margin = margin(t = 0, r = 20, b = 0, l = 0)),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank(), 
          panel.border = element_blank(), 
          panel.grid = element_blank(),
          legend.position = "top",
          legend.text = element_text(size = 14, colour = "black"))

@@

int_function(pm_data_2row, "home_floors_2level", "Floors in home")
int_function(pm_data_2row, "home_sqm_2level", "Home Square Meters")
int_function(pm_data_2row, "education", "Education")
int_function(pm_data_2row, "income_2level", "Income")
int_function(pm_data_2row, "home_year_built_2level", "Year home was built")
int_function(pm_data_2row, "stove_age_2level", "Stove age")
int_function(pm_data_2row, "stove_grade", "Stove grade")
int_function(pm_data_2row, "chimney_clean_3level", "When was chimney cleaned")
int_function(pm_data_2row, "wood_collect_3level", "When was wood collected")
int_function(pm_data_2row, "wood_collect_method", "Wood collect method")
int_function(pm_data_2row, "burn_level_3level", "Burn level")
int_function(pm_data_2row, "residents_smoke", "Residents Smoke")

obs <- pm_data_2row %>% 
  filter(!is.na(outcome)) %>% 
  filter(!is.na(baseline_outcome)) %>%
  filter(!is.na(area)) %>% 
  filter(!is.na(cohort)) %>% 
  filter(!is.na(treatment)) %>% 
  filter(!is.na(wood_collect_method)) %>%
  group_by(wood_collect_method, treatment) %>% 
  count()
obs
save_contrasts
Anova(itt_results_int)

n_table
pm_summary_table
save_summary
save_contrasts_full

@@

# Personal PM2.5 Interaction Analysis
```{r}
# Prep Data
pm_data_2row <- analysis_data %>% 
  mutate(outcome = mp_mean_visit) %>%  # select outcome here
  arrange(area, home, adult_id_char, winter_id, sampling_visit) %>% 
  group_by(area, home, adult_id_char, winter_id) %>% 
  mutate(outcome = if_else(winter_id == 1, mean(outcome, na.rm = T), outcome)) %>% 
  dplyr::select(area, home, adult_id_char, winter_id, sampling_visit, 
                cohort, treatment, outcome, income, education, residents_smoke, 
                home_sqm_2level, burn_level, gender, chimney_clean, stove_age, 
                stove_grade, age, bmi, visit_intervention_diff, 
                treatment_filter_type, filter_compliance, kw_perc_expected,
                burn_level_3level, chimney_clean_3level, age_2level,
                bmi_2level, income_2level, income_3level, stove_age_2level,
                hypertension, wood_collect_3level, home_year_built_2level,
                steps, steps_2level, steps_4level,
                home_floors_2level, wood_collect_method) %>% 
  ungroup() %>% 
  distinct(area, home, winter_id, sampling_visit, .keep_all = T) %>% 
  group_by(area, home) %>% 
  pivot_wider(names_from = "winter_id", values_from = "outcome") %>% 
  arrange(area, home, sampling_visit) %>% 
  mutate(outcome = `2`,
         baseline_outcome = `1`,
         baseline_outcome = if_else(is.na(baseline_outcome), first(baseline_outcome),
                                    baseline_outcome)) %>% 
  replace_with_na(replace = list(baseline_outcome = NaN, outcome = NaN)) %>% 
  filter(visit_intervention_diff != 9999) %>% 
  ungroup()

save_contrasts <<- confint(int_emmeans$contrasts) %>% 
  mutate(estimate = round((exp(estimate)-1)*100, digits = 2),
         conf.low = round((exp(lower.CL)-1)*100, digits = 2),
         conf.high = round((exp(upper.CL)-1)*100, digits = 2)) %>% 
  dplyr::select(contrast, int_var, estimate, conf.low, conf.high)

plot_results <- save_contrasts %>% 
  ggplot(aes(group = contrast, shape = contrast)) +
  geom_point(aes(x=int_var, y=estimate), 
             position = position_dodge(width = 0.5), size = 4) +
  geom_errorbar(aes(x=int_var, ymin=conf.low, ymax=conf.high), 
             position = position_dodge(width = 0.5), size = 1.2, width = 0.5) +
  geom_hline(yintercept = 1) +
  theme_bw() +  
  ggtitle(label = "Interaction contrasts, ITT framework, Personal PM",
          subtitle = paste0("Interaction term = ", interaction_label)) +
  labs(y = "% difference") +
  labs(x = "", group = "", shape = "") +
  theme(title = element_text(size = 16), 
          axis.text.x = element_text(size = 16, colour = "black", angle = 45,
                                     hjust = 1, vjust = .8),
          axis.text.y = element_text(size = 16, colour = "black"),
          axis.title.y = element_text(size = 16,
                                      margin = margin(t = 0, r = 20, b = 0, l = 0)),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank(), 
          panel.border = element_blank(), 
          panel.grid = element_blank(),
          legend.position = "top",
          legend.text = element_text(size = 14, colour = "black"))

int_function(pm_data_2row, "home_floors_2level", "Floors in home")
int_function(pm_data_2row, "home_sqm_2level", "Home Square Meters")
int_function(pm_data_2row, "education", "Education")
int_function(pm_data_2row, "income_2level", "Income")
int_function(pm_data_2row, "home_year_built_2level", "Year home was built")
int_function(pm_data_2row, "stove_age_2level", "Stove age")
int_function(pm_data_2row, "stove_grade", "Stove grade")
int_function(pm_data_2row, "chimney_clean_3level", "When was chimney cleaned")
int_function(pm_data_2row, "wood_collect_3level", "When was wood collected")
int_function(pm_data_2row, "wood_collect_method", "Wood collect method")
int_function(pm_data_2row, "burn_level_3level", "Burn level")
int_function(pm_data_2row, "residents_smoke", "Residents Smoke")
int_function(pm_data_2row, "steps_2level", "Fitbit Steps - 2 Level")
int_function(pm_data_2row, "steps_4level", "Fitbit Steps - 4 Level")

obs <- pm_data_2row %>% 
  filter(!is.na(outcome)) %>% 
  filter(!is.na(baseline_outcome)) %>%
  filter(!is.na(area)) %>% 
  filter(!is.na(cohort)) %>% 
  filter(!is.na(treatment)) %>% 
  filter(!is.na(wood_collect_method)) %>%
  group_by(wood_collect_method, treatment) %>% 
  count()
obs
save_contrasts
Anova(itt_results_int)

n_table
pm_summary_table
save_summary
save_contrasts_full
